Assignment 2

### 2019-06-29 ex2/report/report.tex
Added logreg pref

>>>>

 \begin{table}
 \caption{Logistic regression performance when trained with predictions from random forests, deep learning and real labels.}
 \label{tab:logreg_results}
 \begin{tabular}{l r r r} \toprule
 & RF predictions & DL prediction & Real labels \\
 Accuracy	&	0,9619 $\pm$ 0,0009	&	0,9670 $\pm$ 0,0002	&	0,9621 $\pm$ 0,0010	\\
Precision	&	0,9049 $\pm$ 0,0013	&	0,9140 $\pm$ 0,0007	&	0,9047 $\pm$ 0,0018	\\
Recall	&	0,9487 $\pm$ 0,0024	&	0,9585 $\pm$ 0,0016	&	0,9499 $\pm$ 0,0020	\\
F1 score	&	0,9262 $\pm$ 0,0017	&	0,9357 $\pm$ 0,0004	&	0,9268 $\pm$ 0,0019	\\
Youden's J	&	0,9151 $\pm$ 0,0027	&	0,9283 $\pm$ 0,0013	&	0,9161 $\pm$ 0,0027	\\
\bottomrule
\end{tabular}
\end{table}
